---
title: "Assignment 1"
---

My first assignment has two parts.

## (a)

I chose the video where Baykal Hafizoglu was the guest.

**Summary**

To begin with, Baykal Hafizoglu introduced himself. He talked about his academic achievements, work experiences and hobbies. He talked about the projects that took part in. He mentioned that he was both the owner and developer of a program called Supply Chain Solver. Secondly, he talked about data analytics world. He divided the analytics world in four pieces such as Descriptive, Diagnostic, Predictive, Prescriptive. He even compared Prescriptive Analytics to a doctor writing a prescription.He related the data analytics world pieces to the industrial engineering courses and emphasized the importance of these relationships. Thirdly, he talked about analytical solutions and methods. He gave some examples which is given at daily life about analytical methods. In addition, he talked about his obtainments. He recommended defining the problem first in all cases. He suggested that if I was developing a model, I should share that model with people. He said that staying on the computer would not be beneficial. He said that if I am doing a job, I have to present it in a language that everyone can understand. He said that after all the work, it would be useful to go back to problem definition. Finally, He answered questions from students such as Aykut.

**First Question**

1)  Can you give an example of the Descriptive-\>Predictive-\>Prescriptive process from your daily life?

*Answer:* "Daily Inventory Level -\> Demand Forecast -\> Safety Stock Optimization" or "Mortgage Application -\> Applicant's Loan Score Estimation -\> Mortgage Decision"

**Second Question**

2)  What is KPI short for?

<!-- -->

a)  Key Personalizing Index

b)  Kit Personal intensiveness

c)  Key Performance Indicator **(This is the answer)**

d)  Knot Pair Import

## (b)

I explained it step by step using code chunks.

**First Step**

We need a uploading dslabs library if is not included . Task 1: Import the 'polls_us_election_2016' data set from dslabs.

```{r}
library(dslabs)
data(polls_us_election_2016)
```

**Second Step**

Task 2: Display the first 10 rows of the data set on your web page.

```{r}
head(polls_us_election_2016, 10)
```

**Third Step**

Task 3: Calculate and display the total number of NA values in the entire data set. I used is.na function. I knew this function from lecture slides and Aykut's Website. (By the way, Aykut's Website is superfly)

```{r}
total_number_of_none_available <- sum(is.na(polls_us_election_2016))
print(total_number_of_none_available)
```

**Fourth Step**

Task 4: Replace all NA values with my first name and my birth year. First of all, I  defined two variable which are my first name and my birth year. Secondly, I defined a function which is recursive function type. This function???s mission is to evaluate of data variables equal to NA value or not for  factor columns and this function has ???for loop??? with if-else statement for checking all columns and changing NA values. This function changed all NA values in numeric columns, character columns and factor columns with my birth yera and my first name. Finally, I assigned a variable which is equal to changed data by this function. In this part, I take some helps from slides, AI tools, datacamp lectures and friends about loop structure, function structure, use of if-else statement, use of return statement, use of squared brackets and use of levels function. Especially, I used AI on using for loop. I know for loops structure, but using if-else and functions inside each other in the for loop structure was very difficult for me. Recursive function idea was coming from my mind after 20 or 30 trials. Most of my error is state values changed by numeric value. I still don't understand why I'm getting an error.

```{r}
birth_year <- 2003
first_name <- "Mustafa"


replace_na_general <- function(data, birth_year, first_name) {
  
  
  replace_na_in_factor <- function(factor_col, replacement) {
    levels(factor_col) <- c(levels(factor_col), replacement) 
    factor_col[is.na(factor_col)] <- replacement             
    return(factor_col)
  }
  
  
  for (col in names(data)) {
    if (is.numeric(data[[col]])) {
      
      data[[col]][is.na(data[[col]])] <- birth_year
    } else if (is.character(data[[col]])) {
      
      data[[col]][is.na(data[[col]])] <- first_name
    } else if (is.factor(data[[col]])) {
      
      data[[col]] <- replace_na_in_factor(data[[col]], first_name)
    }
  }
  
  return(data)  # G??ncellenen veri ??er??evesini d??nd??r
}

modified_data <- replace_na_general(polls_us_election_2016, birth_year, first_name)
```

I checked in step five whether the code worked or not.

**Fifth Step**

Task 5: Print the first 10 rows of the new data frame and the total number of NAs remaining in the new data frame. In this step, I checked the code about working correctly. If the result is equal to 0, we have no NA values. They have all changed. I remember we did this kind of check in class. I used head function again for new data.

```{r}
total_na_number_new <- sum(is.na(modified_data))
print(total_na_number_new)

head(modified_data, 10)
```

