---
title: "Assignment 1"
---

My first assignment has two parts.

## (a) 
I chose the video where Baykal Hafizoglu was the guest.

**Summary**

To begin with, Baykal Hafizoglu introduced himself. He talked about his academic achievements, work experiences and hobbies. He talked about the projects that took part in. He mentioned that he was both the owner and developer of a program called SupplY Chain Solver.Secondly, he talked about data analytics world. He divided the analytics world in four pieces such as Descriptive, Diagnostic, Predictive, Prescriptive. He even compared Prescriptive Analytics to a doctor writing a prescription.He related the data analytics world pieces to the industrial engineering courses and emphasized the importance of these relationships.Thirdly, he talked about analytical solutions and methods. He gave some examples which is given at daily life about analytical methods.
In addition, he talked about his obtainments.He recommended defining the problem first in all cases. He suggested that if I was developing a model, I should share that model with people. He said that staying on the computer would not be beneficial. He said that if I am doing a job, I have to present it in a language that everyone can understand. He said that after all the work, it would be useful to go back to problem definition. Finally, He answered questions from students such as Aykut.

**First Question**

1) Can you give an example of the Descriptive->Predictive->Prescriptive process from your daily life?

*Answer:* "Daily Inventory Level -> Demand Forecast -> Safety Stock Optimization" or "Mortgage Application -> Applicant's Loan Score Estimation -> Mortgage Decision"

**Second Question**

2) What is KPI short for?

a) Key Personalizing Index

b) Kit Personal intensiveness

c) Key Performance Indicator

d) Knot Pair Import

## (b)

I explained it step by step using code chunks.

**First Step**
```{r}
# We need a library
library(dslabs)
# Import the 'polls_us_election_2016' data set from dslabs
data(polls_us_election_2016)
```

**Second Step**
```{r}
# Display the first 10 rows of the data set on your web page.
head(polls_us_election_2016, 10)# head function from second week slide and help part

```

**Third Step**
```{r}
# Calculate and display the total number of NA values in the entire data set
total_number_of_na <- sum(is.na(polls_us_election_2016))
print(total_number_of_na)
```

**Fourth Step**

- in progress

**Fifth Step**

- in progress


